\begin{abstract}
    % Your abstract goes here. This should be about 2-3 paragraphs summarising the motivation for 
    % your project and the main outcomes (software, results, etc.) of your project. 
    Zero-knowledge proofs are protocols that allow a prover to prove the validity of a 
    statement to a verifier without revealing any information about the statement. There has 
    been a long line of research into zero-knowledge proofs -- 
    in particular, zero-knowledge proofs for disjunctive statements have been a core target. 
    Disjunctive statements are made up of a set of clauses joined by logical OR operators, 
    and the goal of the prover is to prove that at least one of the clauses is true. 
    
    In this work we focus on one approach for constructing disjunctive zero-knowledge proofs: 
    general \emph{compilers} for zero-knowledge proofs. This approach has been explored by in early work by 
    Cramer and Damg{\aa}rd
    in \textquote{Proofs of Partial Knowledge and Simplified Design of Witness Hiding Protocols}, 
    and more recently by Goel {\em et al.} in \textquote{Stacking Sigmas: A Framework to Compose 
    $\Sigma$-Protocols for Disjunctions}. We implement the compilers 
    proposed in these two papers, benchmark their performance, and compare the results. 
    There has been a lack of implementations of these compilers, and this project serves to fill 
    in this gap, as well as to provide a better understanding of their performances, and 
    lay the groundwork for future work to benchmark against past work. 

    Our results validate that Goel {\em et al.}'s compiler, Stacking Sigmas, outperforms Cramer and 
    Damg{\aa}rd's compiler, CDS94, in terms of communication complexity as the number of clauses increase. 
    We also show that the choice of secret sharing scheme influences the 
    computational complexity of the CDS94 protocol greatly. 
    % Additionally, we show that by comparing the raw size of the proof, 
    % Stacking Sigmas provides significant savings over CDS94. 
\end{abstract}