% !TeX root = dissertation.tex
Before discussing our implementation and results, we introduce the necessary background concepts for this project. 
We first formalise the notation we use in this report and highlight broad concepts that are relevant to the entire project. 
These concepts include zero-knowledge, disjunctive zero-knowledge, and $\Sigma$-protocols. 
After which, we split the remaining section into subsections: 
each for one of the compilers we implement \cite{CDS94, StackingSigmas}%, SpeedStacking}.

\section{Notation \& Terminology}\label{sec:notation}
\begin{table}[h]
  \centering
  \label{tab:notation}
  \caption{Notation used in this report}
  \begin{tabular}{|A{0.1\linewidth}|M{0.8\linewidth}|}
    \hline
    Symbol & Details \\\hline
    $\lambda$ & Computational security parameter. This refers to the ability of a cryptographic system to remain secure against an adversary who is computationally bounded. \\\hline
    $\kappa$ & Statistical security parameter. This pertains to the security provided by negligible statistical probability. \\\hline
    $\verify$ & Boolean assertion. \\\hline
    $\|$ & Bit concatenation: $0000 \| 1111 = 00001111$ \\\hline
    $\samplefrom$ & Sampling from a distribution. $x \samplefrom \mathcal D$ means that we sample $x$ from 
    the distribution "$\mathcal D$". \\
    \hline
    $[l]$ & The range of integers from 1 to $l$ \\
    \hline
  \end{tabular}
\end{table}

Throughout this paper, when "randomness" is mentioned in the definition of certain protocols, it usually refers to random bits generated by random number generators (RNG).

\input{background/disjunctive-zero-knowledge.tex}

\input{background/sigma.tex}
\input{background/schnorr.tex}

% CDS %
\section{CDS94}
In this section, we introduce the components necessary for the \cite{CDS94} compiler. In addition to a $\Sigma$-protocol, which 
is relevant to every compiler in this project, the CDS94 compiler requires a \emph{secret sharing scheme} and the compiler 
itself. In the following 2 subsections, we introduce these components.
\input{background/secret-sharing.tex}
\input{background/cds-compiler.tex}

% Stacking Sigmas %
\section{Stacking Sigmas}
Moving on, we introduce the concept of a \emph{partially-binding vector commitment scheme} 
and present the Stacking Sigmas compiler proposed by \cite{StackingSigmas}. This compiler aims to improve on the 
communication complexity of the \cite{CDS94} compiler, by reducing the communication size to $O(\log n)$, where $n$ is the 
number of clauses in the disjunction. 
% Partially Binding Vector Commitment from Discrete Log
\input{background/comm_scheme.tex}
% Section on stacking sigmas - talk about how stacking works
\input{background/stackable.tex}

% Speed Stacking %
% \input{background/homomorphisms.tex}
% % section on compressed sigma protocols (compression mechanism)
% \input{background/compressed_sigma.tex}
% % section on speed stacking compiler 
% \input{background/speed-stacker.tex}

